\textbf{Computational Fuzzy Extractors}

### 2013-05-17 CompFuzzExt.tex
working on 4.4

\subsection{Comparison with computational extractor based construction}
\label{sec:prg based comparison}
In this section, we constructed a computational fuzzy extractor by making the whole process ``computational.''  Alternatively, a computational fuzzy extractor could be constructed by using a computational extractor~\cite{krawczyk2010cryptographic} in place of the information-theoretic randomness extractor.  A simple example of a computational extractor is the \emph{extract-then-expand} mechanism: a pseudorandom generator is applied to the output of a information-thereotic randomness extractor. 
%using an information theoretic fuzzy extractor and then applying a pseudorandom generator to the output of the fuzzy extractor.  This is the extract-then-expand computational extractor suggested by Krawczyk in~\cite{krawczyk2010cryptographic}.  
Under the same hardness of approximating GAPSVP and SIVP, Applebaum et. al. achieve a pseudorandom generator with linear stretch~\cite{applebaum2006pseudorandom}.  They consider $\vA$ as a public value and show a setting of parameters where $f_\vA(x, e) = \vA x + e$ is a pseudorandom generator with linear stretch.  Likewise, by increasing the field size in \consref{cons:informal construction}, it is possible to output a linear factor of the number of input bits~(see \secref{sec:parameter settings}).  Both techniques are able to produce a linear stretch on the entropy of the source.

@@

\begin{figure}[t]
\begin{framed}
\begin{enumerate}
\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve'$.
\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$. Initialize $\vW \in \Fq^{n\times (\alpha+\beta)}$ to be the zero matrix.
\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
\item Randomly generate $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$.
		\subitem If $\rank(\vect{S})<\alpha$, stop and output a random bit.
\item Find a set of $\alpha$ linearly independent columns in $\vS$.  Let $T$ be the set of these indices.
\item For all $x_i$ where $n\leq i$ and $i\not \in T$:\label{step:fill in matrix}
\subitem Generate $x_i\overset{\$}\leftarrow \Fq$.  
\subitem For $j=1,..., m$:
\subsubitem Generate $\vW_{j, i}\overset{\$}\leftarrow \Fq$
\subsubitem Set $b_j^* = b_j^* + \vW_{j, i} x_i$.
\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \vW\\\hline \vR & \vS\end{array}\right)$.
\item \label{step:randomization}
For {$i=1,..., m$}:
\subitem Randomly generate $\gamma_i \leftarrow \Fq^{1 \times \alpha}$.
\subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+k})$
\item Run $D$ on input $\vA, \vb$.
\item Output $D$'s output.
\end{enumerate}
\end{framed}
\caption{A PPT $D'$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
\label{fig:perfectLWEreduction}
\end{figure}
The distinguisher $D'$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability~(techniques from Cooper~\cite{cooper2000rank}):
\begin{claim}
\label{cl:full rank matrix}
Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
\end{claim}
\begin{proof}
The probability that all $\alpha$ rows are linearly independent is the successive probability that each row is linearly independent of the previous rows, for the $i$th row this probability is $q^{i-1}/q^{\alpha+\beta}$.  By union bound and $\beta = \omega(1)$, the probability that $\vS$ is not full rank is:
\begin{align*}
\Pr[\rank(\vS) < \alpha] &= \sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
\leq \alpha \frac{q^{\alpha}}{q^{\alpha+\beta} }=\ngl(n)\\
\end{align*}
Thus, $\Pr[\rank(\vS) = \alpha] \geq 1-\ngl(n)$.
\end{proof}
\begin{corollary}
$
|\Pr[D(\vA, \vA\vx+\ve) = 1  | \rank(\vS) = \alpha] - \Pr[D(\vA, \vu) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
$
\end{corollary}

>>>>

\subsection{Comparison with computational-extractor-based constructions}
\label{sec:prg based comparison}
As we already mentioned in the introduction, an alternative approach to building a computational fuzzy extractor is to use  a computational extractor (e.g.,~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational}) in place of the information-theoretic extractor in the sketch-and-extract construction.  We will call this approach \emph{sketch-and-comp-extract}.  (A simple example of a computational extractor is a pseudorandom generator applied to the output of an information-theoretic extractor; but other approaches are also possible.)
%using an information theoretic fuzzy extractor and then applying a pseudorandom generator to the output of the fuzzy extractor.  This is the extract-then-expand computational extractor suggested by Krawczyk in~\cite{krawczyk2010cryptographic}.

This approach (specifically, its analysis via \lemref{lem:fuzzy ext construction}) works as long as the amount of entropy $\tilde{m}$ of $w$ conditioned on the sketch $s$ remains high enough to run a computational extractor.  However, $\tilde{m}$ decreases with the error parameter $t$ due to coding bounds, and it is conceivable that, if $W$ has just barely enough entropy to begin with, it will have too little entropy left to run a computational extractor once $s$ is known.

In contrast, in our approach, the entropy of $w$ conditioned on $p=(\vA, \vA X+w)$ is not relevant to security, because we do not extract from $w$. Instead, we require that $w$ is not recoverable computationally given $p$.  Note that this requirement does not imply that $w$ can be extracted from, because computational extractors may require a longer minimum input length than the computational entropy of $w$.   Our approach works in such a setting because instead of extracting from $w$, we hide secret randomness using $w$.

The main advantage of our analysis (instead of sketch-and-comp-extract) is that security need not depend on the decoding radius $t$.  Our codes (namely, random linear codes) can tolerate very high $t$, in fact.  In the case of secure sketches, codes tolerating such high $t$ would leave little entropy in $w$.  In our construction, the decoding radius depends only on the best available decoding algorithm for random linear codes.

\lnote{use any of the below?}
 utilize secret randomness to obtain the key $r$, and hide that randomness using $w$.

The code defined by $\vA$ can correct very high

Under the same hardness of approximating GAPSVP and SIVP, Applebaum et. al. achieve a pseudorandom generator with linear stretch~\cite{applebaum2006pseudorandom}.  They consider $\vA$ as a public value and show a setting of parameters where $f_\vA(x, e) = \vA x + e$ is a pseudorandom generator with linear stretch.  Likewise, by increasing the field size in \consref{cons:informal construction}, it is possible to output a linear factor of the number of input bits~(see \secref{sec:parameter settings}).  Both techniques are able to produce a linear stretch on the entropy of the source.

@@

\begin{figure}[p]
\begin{framed}
\begin{enumerate}
\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve'$.
\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$. Initialize $\vW \in \Fq^{n\times (\alpha+\beta)}$ to be the zero matrix.
\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
\item Randomly generate $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$.
		\subitem If $\rank(\vect{S})<\alpha$, stop and output a random bit.
\item Find a set of $\alpha$ linearly independent columns in $\vS$.  Let $T$ be the set of these indices.
\item For all $x_i$ where $n\leq i$ and $i\not \in T$:\label{step:fill in matrix}
\subitem Generate $x_i\overset{\$}\leftarrow \Fq$.  
\subitem For $j=1,..., m$:
\subsubitem Generate $\vW_{j, i}\overset{\$}\leftarrow \Fq$
\subsubitem Set $b_j^* = b_j^* + \vW_{j, i} x_i$.
\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \vW\\\hline \vR & \vS\end{array}\right)$.
\item \label{step:randomization}
For {$i=1,..., m$}:
\subitem Randomly generate $\gamma_i \leftarrow \Fq^{1 \times \alpha}$.
\subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+k})$
\item Run $D$ on input $\vA, \vb$.
\item Output $D$'s output.
\end{enumerate}
\end{framed}
\caption{A PPT $D'$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
\label{fig:perfectLWEreduction}
\end{figure}
The distinguisher $D'$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability~(techniques from Cooper~\cite{cooper2000rank}):
\begin{claim}
\label{cl:full rank matrix}
Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
\end{claim}
\begin{proof}
The probability that all $\alpha$ rows are linearly independent is the successive probability that each row is linearly independent of the previous rows, for the $i$th row this probability is $q^{i-1}/q^{\alpha+\beta}$.  By union bound and $\beta = \omega(1)$, the probability that $\vS$ is not full rank is:
\begin{align*}
\Pr[\rank(\vS) < \alpha] &= \sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
\leq \alpha \frac{q^{\alpha}}{q^{\alpha+\beta} }=\ngl(n)\\
\end{align*}
Thus, $\Pr[\rank(\vS) = \alpha] \geq 1-\ngl(n)$.
\end{proof}
\begin{corollary}
$
|\Pr[D(\vA, \vA\vx+\ve) = 1  | \rank(\vS) = \alpha] - \Pr[D(\vA, \vu) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
$
\end{corollary}
